Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted

### 2015-07-08 MS.tex
References added: in ms (112 instead of 108 articles used in the meta-analyses) in references bibtex (in read and meta-analyses)

\textit{Number of data source references} 108

@@

\item 
Traits should influence growth in a way that depend on individual plants size. We outline mechanisms and hypotheses based on new theory, and test these predictions for five traits using a meta-analysis of 108 studies (\textgreater{} 500 correlations).

@@

We found 108 studies published between between 1983 and 2014 that met our requirements. Climate zones spanned from temperate regions to  tropics (map in Fig. \ref{FigA3}). Different experiment types (laboratory, field, plantation or greenhouse) and growth measurements were included (see Fig. \ref{FigA7} for analyses of how these factors affected  correlations between growth and traits). Given this variety, it was not surprising to find wide ranges of r reported for all traits. For instance,  r varied from -0.98 to 0.99 for SLA, and from -0.74 to 0.74 for WD (Fig. \ref{FigA4}). Number of species used for each correlation ranged from 1 to 300 species with average  31. As expected the correlation coefficient varied less widely as sample size increased (funnel plots Fig. \ref{FigA8}). In the analyses described in Figs 2, A5 and A6 coefficients were weighted according to sample size, making the small-sample extremes less influential. Funnel plots exhibited a typical funnel shape for all five functional traits analyzed, showing no evidence for publication bias (Fig. \ref{FigA8}).

@@

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA4.pdf}
\caption{\textbf{Range of the correlation of correlations (r) between
growth and trait across the world} Coefficients of correlation (r)
between the plant growth and \textbf{a)} Specific leaf area (SLA, n=
111), \textbf{b)} Wood density (WD, n=64), \textbf{c)} Asymptotic
maximum height (Hmax, n=23), \textbf{d)} Seed mass (Seedmass, n=36 and
\textbf{e)} Rate of CO2 assimilation (Aarea, n=24) reported from 108
articles. Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
is proportional to its weights in the meta-analysis. The colors
correspond to the stage for which the r values have been recorded: red
points corresponds adult stage, orange points to saplings, and grey
points to juveniles.}
\label{FigA4}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA5.pdf}
\caption{\textbf{Mean coefficient correlation r (+SD) between growth
rate and traits, established from 108 articles.} The mean
coefficients are weighted by sample size (i.e number of species used to
perform the correlation), and calculated both across all plant stages
and for each stage. Each panel corresponds to a functional trait:
\textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD),
\textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass,
\textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate
of CO2 (Aarea). Shown here are ideal dataset (recorded at interspecific level and under unstressed  conditions)}
\label{FigA5}
\end{figure}

>>>>

\textit{Number of data source references} 112

@@

\item 
Traits should influence growth in a way that depend on individual plants size. We outline mechanisms and hypotheses based on new theory, and test these predictions for five traits using a meta-analysis of 112 studies (\textgreater{} 500 correlations).

@@

We found 112 studies published between between 1983 and 2014 that met our requirements. Climate zones spanned from temperate regions to  tropics (map in Fig. \ref{FigA3}). Different experiment types (laboratory, field, plantation or greenhouse) and growth measurements were included (see Fig. \ref{FigA7} for analyses of how these factors affected  correlations between growth and traits). Given this variety, it was not surprising to find wide ranges of r reported for all traits. For instance,  r varied from -0.98 to 0.99 for SLA, and from -0.74 to 0.74 for WD (Fig. \ref{FigA4}). Number of species used for each correlation ranged from 1 to 300 species with average  31. As expected the correlation coefficient varied less widely as sample size increased (funnel plots Fig. \ref{FigA8}). In the analyses described in Figs 2, A5 and A6 coefficients were weighted according to sample size, making the small-sample extremes less influential. Funnel plots exhibited a typical funnel shape for all five functional traits analyzed, showing no evidence for publication bias (Fig. \ref{FigA8}).

@@

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA4.pdf}
\caption{\textbf{Range of the correlation of correlations (r) between
growth and trait across the world} Coefficients of correlation (r)
between the plant growth and \textbf{a)} Specific leaf area (SLA, n=
111), \textbf{b)} Wood density (WD, n=64), \textbf{c)} Asymptotic
maximum height (Hmax, n=23), \textbf{d)} Seed mass (Seedmass, n=36 and
\textbf{e)} Rate of CO2 assimilation (Aarea, n=24) reported from 112
articles. Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
is proportional to its weights in the meta-analysis. The colors
correspond to the stage for which the r values have been recorded: red
points corresponds adult stage, orange points to saplings, and grey
points to juveniles.}
\label{FigA4}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA5.pdf}
\caption{\textbf{Mean coefficient correlation r (+SD) between growth
rate and traits, established from 112 articles.} The mean
coefficients are weighted by sample size (i.e number of species used to
perform the correlation), and calculated both across all plant stages
and for each stage. Each panel corresponds to a functional trait:
\textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD),
\textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass,
\textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate
of CO2 (Aarea). Shown here are ideal dataset (recorded at interspecific level and under unstressed  conditions)}
\label{FigA5}
\end{figure}
